---
output: pdf_document
geometry: "top=1.5cm,left=2.5cm,right=2.5cm"
params:
  chem_name: ""
  cas_num: ""
  af_table: data.frame(x = 1)
  af: "1"
  trophic_sp_table: data.frame(x = 1)
  trophic_grp_table: data.frame(x = 1)
  method: ""
  benchmark: data.frame(ctv_est_mg.L = 1)
  gp_result: NULL
---

<!-- # Copyright 2023 Province of British Columbia -->
<!-- #  -->
<!-- # Licensed under the Apache License, Version 2.0 (the "License"); -->
<!-- # you may not use this file except in compliance with the License. -->
<!-- # You may obtain a copy of the License at  -->
<!-- #  -->
<!-- # http://www.apache.org/licenses/LICENSE-2.0 -->
<!-- #  -->
<!-- # Unless required by applicable law or agreed to in writing, software -->
<!-- # distributed under the License is distributed on an "AS IS" BASIS, -->
<!-- # WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied. -->
<!-- # See the License for the specific language governing permissions and -->
<!-- # limitations under the License. -->

# Aquatic Life Water Quality Benchmark Report

`r format(as.POSIXct(as.numeric(as.POSIXct(Sys.time())), tz = 'Etc/GMT+8', origin = '1970-01-01'), '%B %d, %Y')`  
Chemical: `r params$chem_name`    
CAS Number: `r params$cas_num`   

##### Data Summary

```{r, echo=FALSE}
knitr::kable(
  params$trophic_sp_table
)
```

Benchmark derivation method selected: `r params$method`

Critical Toxicity Value (HC5 if method is SSD): 

```{r, echo=FALSE}
knitr::kable(
  params$benchmark
)
```

##### Assessment Factor Summary

```{r, echo=FALSE}
knitr::kable(
  params$trophic_grp_table
)
```

##### Recommended Assessment Factors

```{r, echo=FALSE}
knitr::kable(
  params$af_table
)
```

##### Final Aquatic Life Water Quality Benchmark  
$\\$
Aquatic life water quality benchmark ($WQ_{AL}$) = critical toxicity value $\div$ assessment factor

$WQ_{AL} =$ `r signif(params$benchmark$ctv_est_mg.L)` mg/L $\div$ `r params$af` 

$WQ_{AL} =$  `r signif(params$benchmark$ctv_est_mg.L / params$af)` mg/L 
  
\newpage

```{r, echo=FALSE, fig.width=13.5}
params$gp_result
```

##### Software Versions:

```{r, echo=FALSE, results = 'asis'}
cat("- wqbench:", as.character(packageVersion("wqbench")), "\n")
cat("\n")
cat("- shinywqbench", as.character(packageVersion("shinywqbench")))
```
