---
title: "Aquatic Life Water Quality Benchmark Report"
date: "`r format(as.POSIXct(as.numeric(as.POSIXct(Sys.time())), tz = 'Etc/GMT+8', origin = '1970-01-01'), '%B %d, %Y')`"
output: pdf_document
params:
  chem_name: ""
  method: ""
  benchmark: NULL
  af: NULL
---

Chemical Name: **`r params$chem_name`**

### Data Summary

```{r, echo=FALSE}
knitr::kable(
  tibble::tibble(
    "Trophic Group" = 1,
    "No. of species" = 2
  )
)
```

Benchmark derivation method selected: `r params$method`

Critical Toxicity Value (HC5 if method is SSD): 

```{r, echo=FALSE}
knitr::kable(
  params$benchmark,
  digits = 5
)
```

## Assessment Factor Summary

```{r, echo=FALSE}
knitr::kable(
  tibble::tibble(
    "Consideration" = 1,
    "Result" = 1
  )
)
```

### Recommended Assessment Factors: 

```{r, echo=FALSE}
knitr::kable(
  params$af,
  digits = 1
)
```

### Final Aquatic Life Water Quality Benchmark

Aquatic life water quality benchmark (WQAL) = critical toxicity value รท assessment factor

WQAL = insert CTV รท AF

WQAL = concentration with units






\newpage

Software versions:

```{r, echo=FALSE, results = 'asis'}
cat("- wqbench:", as.character(packageVersion("wqbench")), "\n")
cat("\n")
cat("- shinywqbench", as.character(packageVersion("shinywqbench")))
```

