---
title: "Aquatic Life Water Quality Benchmark Report"
date: "`r format(as.POSIXct(as.numeric(as.POSIXct(Sys.time())), tz = 'Etc/GMT+8', origin = '1970-01-01'), '%B %d, %Y')`"
output: pdf_document
params:
  chem_name: ""
  data: NULL
  method: ""
  benchmark: NULL
---

Chemical Name: **`r params$chem_name`**

##### Data Summary

```{r, echo=FALSE}
knitr::kable(
  wqbench::wqb_summary_trophic_species(params$data)
)
```

Benchmark derivation method selected: `r params$method`

Critical Toxicity Value (HC5 if method is SSD): 

```{r, echo=FALSE}
knitr::kable(
  params$benchmark
)
```

##### Assessment Factor Summary

```{r, echo=FALSE}
knitr::kable(
  wqbench::wqb_summary_trophic_groups(params$data)
)
```

##### Recommended Assessment Factors

```{r, echo=FALSE}
knitr::kable(
  wqbench::wqb_summary_af(params$data)
)
```

##### Final Aquatic Life Water Quality Benchmark  
$\\$
Aquatic life water quality benchmark ($WQ_{AL}$) = critical toxicity value $\div$ assessment factor

$WQ_{AL} =$ `r signif(params$bench$benchmark_est_mg.L*params$bench$af)` mg/L $\div$ `r params$bench$af`

$WQ_{AL} =$  `r signif(params$bench$benchmark_est_mg.L)` mg/L

\newpage

Software versions:

```{r, echo=FALSE, results = 'asis'}
cat("- wqbench:", as.character(packageVersion("wqbench")), "\n")
cat("\n")
cat("- shinywqbench", as.character(packageVersion("shinywqbench")))
```

